\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
\raggedright


\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% BEGIN RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-20pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

    %\small
    %\smallskip
    \vspace*{-40pt}

    \contact{ Saad Quadri}
    {Metuchen NJ, 08840 $\cdot$ (732)~476~8719 \\
    saad@saadquadri.com $\cdot$ github.com/saadq}


    %%%%%%%%%%%%%%%
    %% Education %%
    %%%%%%%%%%%%%%%

    \header{Education}
        \vspace{1mm}
        \textbf{Rutgers University} \hfill \textit{BS Computer Science} \hfill New Brunswick, NJ \hfill Expected: May 2017\\

    \vspace{3mm}

    %%%%%%%%%%%%%%%%%%%%%
    %% Work Experience %%
    %%%%%%%%%%%%%%%%%%%%%

    \header{Work Experience}
        \vspace{1mm}

        \textbf{Mozilla} \hfill \textit{Software Engineer Intern} \hfill Mountain View, CA \hfill Jun 2016 | Aug 2016 \\
        \begin{itemize} \itemsep 3pt
            \item Broadened search criteria for Firefox's context menu to include subdomains in password suggestions.
            \item Refactored disabled-host APIs to use the permission manager for both Firefox and Android's Fennec.
            \item Fixed regressions for Firefox Electrolysis and improved dialogs and notification popups.
        \end{itemize}

        \vspace{1mm}

        \textbf{Codecademy} \hfill \textit{Coding Advisor} \hfill Manhattan, NY \hfill Dec 2015 | May 2016 \\
        \begin{itemize} \itemsep 3pt
            \item Created a JavaScript project for Codecademy Pro members now available in the new JS course.
            \item Taught new coders how to avoid bugs and how to go through the process of fixing existing ones.
            \item Reviewed general programming topics with students and provided assistance for lessons in Java, HTML, CSS, JavaScript, and Ruby.
        \end{itemize}

        \vspace{1mm}

        \textbf{IEEE} \hfill \textit{Software Developer Intern} \hfill Piscataway, NJ \hfill Jun 2015 | Nov 2015 \\
        \begin{itemize} \itemsep 3pt
            \item Wrote an API that allowed CRUD operations to be used for accessing and manipulating data involving current departments/groups/teams at IEEE.
            \item Created a UI for admins that used the aforementioned API to automate the process of syncing departments/groups/teams on the site to relevant databases.
            \item Improved the IEEE Innovate site by using cookies to display tailored web-content.
        \end{itemize}

        \vspace{1mm}

        \textbf{Johnson \& Johnson} \hfill \textit{Web Developer Intern} \hfill New Brunswick, NJ \hfill Jan 2015 | Jun 2015 \\
        \begin{itemize} \itemsep 3pt
            \item Improved existing web pages by migrating inline-styling to external CSS files, and adding cross-browser compatibility.
            \item Created SharePoint front-ends with HTML, CSS, and JavaScript and utilized the jQuery UI library to create responsive widgets.
            \item Debugged original code base as the sole developer on the team and created a standard for SharePoint web part development for future employees.
        \end{itemize}

        \vspace{1mm}


    %%%%%%%%%%%%
    %% Skills %%
    %%%%%%%%%%%%

    \header{Skills}

    {Programming Languages:} $\:$ JavaScript, Java, Ruby, HTML, XML, CSS, Sass \vspace{1mm}
    {\\Frameworks/Libraries:} $\:$ $\:$ $\:$ $\:$Node.js, Koa, Express, React, Redux, jQuery, lodash

    \vspace{4mm}

    %%%%%%%%%%%%%%
    %% Projects %%
    %%%%%%%%%%%%%%

    \header{Projects}
    Source code and other projects available at \sl github.com/saadq \\

    \vspace{2mm}

    {\textbf{Resume Generator} \sl Node.js, Koa, React, Redux} \\
    A webapp for generating LaTeX resumes from form data (including this one). \\

    \vspace{2mm}

    {\textbf{Flow Timer} \sl Node.js, Koa, React, Redux}  \hfill \\

    A modern speedcubing app with a scrambler, timer, and analyzer for cubing statistics. \\

    \vspace{2mm}

    {\textbf{Reddit Image Scraper} \sl Ruby, Sinatra} \hfill \\

    A web app that lets you view a collage of images/videos from a subreddit

    \vspace{2mm}

    {\textbf{Anagrams} \sl HTML, CSS, JavaScript}  \hfill \\

    A cognitive, anagram-recognition game where the player must quickly find the answer. \\

    \vspace{2mm}

    {\textbf{Materialize} \sl XML, JSON} \hfill \\

    A collection of custom themes for Sublime Text, inspired by Material design with 30k+ installations.

\end{document}
