\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
\raggedright


\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-20pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

    %\small
    %\smallskip
    \vspace*{-40pt}

    \contact{ Saad Quadri}
    {Metuchen NJ, 08840 $\cdot$ (732)~476~8719 \\
    saad@saadquadri.com $\cdot$ github.com/saadq}


    %%%%%%%%%%%%%%%
    %% Education %%
    %%%%%%%%%%%%%%%

    \header{Education}

        \vspace{1mm}

        \textbf{Rutgers University} BS Computer Science, New Brunswick, NJ \hfill Expected: May 2017\\


        \vspace{1mm}

        \textbf{Middlesex County College} AS Computer Science, Edison, NJ \hfill May 2015\\

    \vspace{3mm}

    %%%%%%%%%%%%%%%%%%%%%
    %% Work Experience %%
    %%%%%%%%%%%%%%%%%%%%%

    \header{Work Experience}
        \vspace{1mm}
       {\textbf{IEEE}} \hfill \textit{Application Developer} \hfill Piscataway, NJ \hfill Aug 2015 | Present \\
        \vspace{-1mm}
        \begin{itemize} \itemsep 1pt
            \item Created an API that allowed CRUD operations for accessing and manipulating data involving current departments/groups/teams at IEEE.
            \item Developed a UI that allows webadmins to use the aforementioned API to automate the process of syncing departments/groups/teams with relevant databases.
            \item Improved the IEEE Innovate site by using cookies to display tailored web-content.
        \end{itemize}

        {\textbf{IEEE}} \hfill \textit{Application Developer Intern} \hfill Piscataway, NJ \hfill Jun 2015 | Aug 2015 \\
        \vspace{-1mm}
        \begin{itemize} \itemsep 1pt
            \item Created web content with JavaServer Pages and HTML/CSS/JavaScript while following responsive design practices within the Liferay Java CMS.
            \item Redesigned the article template to dynamically create author blocks for each author of an article in order to display their personal info in an organized fashion.
            \item Enhanced sliding carousel for better interaction on mobile and tablet devices.
        \end{itemize}

        {\textbf{Johnson \& Johnson}\hfill \textit{Web Developer Intern} \hfill New Brunswick, NJ \hfill Jan 2015 | Jun 2015 \\
        \vspace{-1mm}
        \begin{itemize} \itemsep 1pt
            \item Improved existing web pages by migrating inline-styling to external CSS files, and adding cross-browser compatibility.
            \item Created SharePoint front-ends with HTML, CSS, and JavaScript and utilized the jQuery UI library to create responsive widgets.
            \item Debugged original code base as the sole developer on the team and created a standard for SharePoint web part development for future employees.
        \end{itemize}


    %%%%%%%%%%%%
    %% Skills %%
    %%%%%%%%%%%%

    \header{Skills}

    {Programming Languages:} $\:$ Java, JavaScript/Node.js, Ruby, XML, HTML, SASS, CSS \vspace{1mm}
    {\\Frameworks/Libraries:} $\:$ $\:$ $\:$ $\:$Express, React, Sinatra, jQuery, Bootstrap, Materialize\vspace{1mm}
    {\\Software/Tools/IDEs:} $\:$ $\:$ $\:$ $\:$ Terminal, Sublime Text, Vim, Eclipse, Git, SVN, MongoDB

    \vspace{4mm}

    %%%%%%%%%%%%%%
    %% Projects %%
    %%%%%%%%%%%%%%

    \header{Projects}
    Source code and other projects available at github.com/saadq \\
    \vspace{2mm}
    {\textbf{Cube Graphs} \sl Node.js, Express, React, Chart.js, MongoDB}  \hfill git.io/vCtnh \\
    A Rubik's Cube timer for speedcubers that visualizes a user's cubing stats with graphs.  \\

    \vspace{2mm}

    {\textbf{Reddit Scraper} \sl Ruby, Sinatra}  \hfill git.io/vmzmQ  \\

    A Sinatra web app that lets the user easily view images/videos from a subreddit. \\

    \vspace{2mm}

    {\textbf{Personal Website} \sl Jekyll}  \hfill saadquadri.com  \\
    A minimal, responsive portfolio website used to display and host projects. \\

    \vspace{2mm}

    {\textbf{Anagrams} \sl HTML, CSS, JavaScript}  \hfill git.io/vmzqj  \\

    A cognitive, anagram-recognition game where the player must quickly find the answer. \\

    \vspace{2mm}

    {\textbf{Hex Guess} \sl HTML, CSS, JavaScript} \hfill git.io/vmzWO \\

    A game that tests the player's knowledge of hexadeximal color values.

    \vspace{2mm}

    {\textbf{Materialize} \sl XML, JSON} \hfill git.io/vnv9F \\

    A collection of custom themes and color schemes for Sublime Text, inspired by Material design.

\end{document}
