\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Saad Quadri}{\href{http://saadquadri.com}{saadquadri.com} | \href{http://github.com/saadq}{github.com/saadq} \\
\href{mailto:saad@saadquadri.com}{saad@saadquadri.com} | (732) 476-8719 \\
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\vspace{1mm}

\runsubsection{Rutgers University}
\descript{| BS Computer Science \hfill New Brunswick, NJ \hfill Exp: May 2017}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\vspace{1mm}

\runsubsection{Codecademy}
\descript{| Engineering Advisor \hfill Manhattan, NY \hfill Jan 2016 – Present}
\vspace{1mm}
\begin{tightemize} \itemsep 7pt
\item Aided students in learning specifcs for languages such as JavaScript, Ruby, Python, and Java.
\item Reviewed coding topics with new students one-on-one and aided in learning programming fundamentals.
\item Taught new coders how to avoid potential bugs and how to go through the process of fixing existing ones.
\end{tightemize}
\sectionsep

\runsubsection{IEEE}
\descript{| Application Developer \hfill Piscataway, NJ \hfill Aug 2015 – Jan 2016}
\vspace{1mm}
\begin{tightemize} \itemsep 7pt
\item Wrote a wrapper around an API that allowed CRUD operations to be used for accessing and manipulating data involving current departments, groups, and teams at IEEE with Java.
\item Created a UI for admins that used the aforementioned API to automate the
process of syncing departments, groups, and teams on the site to relevant databases.
\item Improved the IEEE Innovate site by using cookies to display tailored web-content.
\end{tightemize}
\sectionsep

\vspace{1mm}

\runsubsection{IEEE}
\vspace{1mm}
\descript{| Application Developer Intern \hfill Piscataway, NJ \hfill Jun 2015 – Aug 2015 }
\begin{tightemize} \itemsep 7pt
\item Created web content with JavaServer Pages and HTML/CSS/JavaScript while
following responsive design practices within the Liferay Java CMS.
\item Redesigned the article template to dynamically create author blocks for each
author of an article in order to display their personal info in an organized fashion.
\item Enhanced multiple websites for better interaction on mobile and tablet devices.
\end{tightemize}
\sectionsep

\vspace{1mm}

\runsubsection{Johnson \& Johnson}
\vspace{1mm}
\descript{| Web Developer Intern \hfill New Brunswick, NJ \hfill Jan 2015 – Jun 2015}
\begin{tightemize} \itemsep 7pt
\item Improved existing web pages by migrating inline-styling to external CSS files,
and adding cross-browser compatibility.
\item Created SharePoint front-ends with HTML, CSS, and JavaScript and utilized the jQuery UI library to create responsive widgets.
\item Debugged original code base as the sole developer on the team and created a standard for SharePoint web part development for future employees.
\end{tightemize}

\begin{minipage}[t]{.3\textwidth}
\section{Skills}
\descript{Languages}
Java, JavaScript, Ruby, HTML, XML, CSS, Python

\vspace{2mm}

\descript{Frameworks/Libraries}
Node, Express, React, Redux, jQuery, underscore, Sinatra

\vspace{2mm}

\descript{Software}
Command Line, Git/GitHub, SVN, MongoDB, Sublime Text, Vim

\end{minipage}
\hfill
\begin{minipage}[t]{.65\textwidth}
\section{Projects}
\descript{Flow Timer \textrm{– Node.js, Express, MongoDB, React, and Redux}}
A speedcubing app with user profiles, stats, graphs, and extensive customizability.

\vspace{2mm}

\descript{Reddit Scraper \textnormal{– Ruby, Sinatra}}
A web app that lets you view a collage of images/videos from a subreddit.

\vspace{2mm}

\descript{Materialize \textnormal{– XML, JSON}}
A set of elegant themes for ST3 based on material design. 7k+ installations.

\vspace{2mm}

\descript{Anagrams \textnormal{– HTML, CSS, JavaScript}}
A cognitive recognition game where the player must quickly find the answer.

\end{minipage}

\end{document}  \documentclass[]{article}
%